---
output: github_document
---
[![Travis build status](https://travis-ci.org/rstudio/forge.svg?branch=master)](https://travis-ci.org/rstudio/forge)[![Coverage status](https://codecov.io/gh/rstudio/forge/branch/master/graph/badge.svg)](https://codecov.io/github/rstudio/forge?branch=master)[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/rstudio/forge?branch=master&svg=true)](https://ci.appveyor.com/project/rstudio/forge)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# forge

Helper functions to mold values into shape for interoperating with other language runtimes.

## Installation

You can install the development version from GitHub with 

``` r
devtools::install_github("rstudio/forge")
```

## Examples

```{r, message = FALSE}
library(sparklyr)
sc <- spark_connect(master = "local")

spark_vector <- function(sc, x) {
  v <- forge::cast_double_list(x)
  invoke_new(sc, "org.apache.spark.ml.linalg.DenseVector", v)
}

spark_vector(sc, 1:3)
```

---

Please note that the 'forge' project is released with a [Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
